Analysis

### 2020-01-13 production/analysis-cfa.Rmd

---
title: "Analysis"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    theme: flatly
    number_sections: true
    toc: true
    toc_float: true
editor_options: 
  chunk_output_type: console
---

# Análisis PPM-S

@@

```{r}
library(sjPlot)
library(dplyr)
library(lavaan)

@@

dat04 <- data01 %>% filter(Intro==1) %>% select(starts_with("meritv01"),starts_with("meritv02"),starts_with("meritv03_p"))

dat04$perc_effort <- rowSums(dat04[,c(matches(match = "perc_effort",vars = names(dat04)))],na.rm = TRUE)
dat04$perc_talent <- rowSums(dat04[,c(matches(match = "perc_talent",vars = names(dat04)))],na.rm = TRUE)
dat04$perc_wpart  <- rowSums(dat04[,c(matches(match = "perc_wpart" ,vars = names(dat04)))],na.rm = TRUE)
dat04$perc_netw   <- rowSums(dat04[,c(matches(match = "perc_netw"  ,vars = names(dat04)))],na.rm = TRUE)

@@

@@

@@

@@

@@

```{r,results='hold'}
model04.tau01 <- 'perc_merit=~ r1*perc_effort+r1*perc_talent 
                  perc_nmerit=~perc_wpart +perc_netw  
                  pref_merit=~ pref_effort+pref_talent 
                  pref_nmerit=~pref_wpart +pref_netw'

>>>>

---
title: "Analysis"
date: "`r format(Sys.time(), '%d %B, %Y')`"
css: ../style.css
output: 
  html_document:
    theme: flatly
    number_sections: true
    toc: true
    toc_float: true
editor_options: 
  chunk_output_type: console

---
# Análisis PPM-S

@@

```{r}
library(sjPlot)
library(dplyr)
library(lavaan)
library(stargazer)

@@

dat04 <- data01 %>% filter(Intro==1) %>%
  select(starts_with("meritv01"),
         starts_with("meritv02"),
         starts_with("meritv03_p")) 
dat04$perc_effort <- rowSums(dat04[,c(matches(match = "perc_effort",vars = names(dat04)))],na.rm = TRUE)
dat04$perc_talent <- rowSums(dat04[,c(matches(match = "perc_talent",vars = names(dat04)))],na.rm = TRUE)
dat04$perc_wpart  <- rowSums(dat04[,c(matches(match = "perc_wpart" ,vars = names(dat04)))],na.rm = TRUE)
dat04$perc_netw   <- rowSums(dat04[,c(matches(match = "perc_netw"  ,vars = names(dat04)))],na.rm = TRUE)

@@

```{r echo=FALSE,results='asis'}
stargazer(dat01,type = "html")
```

@@

```{r echo=FALSE,results='asis'}
stargazer(dat02,type = "html")
```

@@

```{r echo=FALSE,results='asis'}
stargazer(dat03,type = "html")
```

@@

```{r echo=FALSE,results='asis'}
stargazer(dat04,type = "html")
```

@@

```{r, results='hold'}
model04.tau01 <- 'perc_merit=~ r1*perc_effort+r1*perc_talent 
                  perc_nmerit=~perc_wpart +perc_netw  
                  pref_merit=~ pref_effort+pref_talent 
                  pref_nmerit=~pref_wpart +pref_netw'
